\addcontentsline{toc}{chapter}{Литература}
\begin{thebibliography}{99}

    \bibitem{Tschantz2006}
    Tschantz, M. S. (2006). Javari : Adding Reference Immutability to Java.

    \bibitem{Zibin2007}
	Zibin, Y., Potanin, A., Artzi, S., Kiezun, A., Ernst, M. D., & Kie, A. (2007). Object and Reference Immutability using Java Generics.
	
	\bibitem{Gordon2012}
	Gordon, C. S., Parkinson, M. J., Parsons, J., Bromfield, A., & Duffy, J. (2012). Uniqueness and reference immutability for safe parallelism. ACM SIGPLAN Notices.
	
	\bibitem{Potanin}
	Potanin, A., Ali, M., & Ernst, M. D. (n.d.). Ownership and Immutability in Generic Java.
	
	\bibitem{Lee2002}	
	Boyapati, C., Lee, R. & Rinard, M. (2002). Ownership Types for Safe Programming : Preventing Data Races and Deadlocks.
	
	\bibitem{Pechtchanski2002}
	Pechtchanski, I., & Sarkar, V. (2002). Immutability specification and its applications. Proceedings of the 2002 joint ACM-ISCOPE conference on Java Grande.
	
	\bibitem{Birka2003}
	Birka, A. (2003). Compiler-Enforced Immutability for the Java Language.
	
	\bibitem{Haack2005}
	Haack, C., Poll, E., & Sch, J. (2005). Immutable Objects for a Java-like Language.
	
	\bibitem{Haack2005a}
	Haack, C., & Poll, E. (2005). Type-based Object Immutability with Flexible Initialization.
	
	\bibitem{Ma2007}
	Ma, K.-K., & Foster, J. S. (2007). Inferring aliasing and encapsulation properties for java. ACM SIGPLAN Notices, 42(10), 423.
	
	\bibitem{Luis2007}
	Luis, T., Jr, C., & Ernst, M. D. (2007). Enforcing and Inferring Reference Immutability in Java.
	
	\bibitem{Artzi2007}
	Artzi, S., Kiezun, A., Glasser, D., Ernst, M. D., & Kie, A. (2007). Combined Static and Dynamic Mutability Analysis.
	
	\bibitem{Kjolstad2011}
	Kjolstad, F., Dig, D., Acevedo, G., & Snir, M. (2011). Transformation for class immutability. Proceeding of the 33rd international conference on Software engineering - ICSE  ’11, 61.
		
\end{thebibliography}
